### 2024-10-29 main_widom_morse.tex
refactor intro

\section{Introduction}
A supercritical fluid is a state of matter that occurs when a substance is subjected to temperatures and pressures above its critical point. Below the critical point the substance exhibits a liquid-gas coexistence. At the critical point, the distinction between the liquid and gas phases of a substance disappears, and beyond this point, the substance exists in a single continuous supercritical state. Despite the absence of first-order phase transitions above the critical point, fluids exhibit distinct liquid-like and gas-like behavior under supercritical conditions, and display a unique mix of properties. With densities comparable to liquids they possess low viscosity and high diffusivity like gases resulting in high solvent power. Moreover, the supercritical properties are instantly tunable by changing pressure and temperature. This is the reason why supercritical fluids have diverse applications across various industries \cite{KMLetal14}.

In the context of supercritical fluids, the Widom line, Frenkel line, and percolation line are theoretical and physical constructs used to describe the complex behavior of fluids beyond the critical point.
All three concepts provide a way to describe how fluids behave in the supercritical region, where the traditional liquid-gas phase distinction no longer applies.
The Frenkel line \cite{BGMetal17} focuses on the dynamics of molecular motion, separating regimes where the fluid behaves more like a liquid (with oscillatory molecular motion) from those where it behaves more like a gas (with only diffusive motion). The percolation line \cite{CKS01} is related to spatial structures, marking the threshold where clusters of fluid or density fluctuations start forming a continuous, system-spanning network.

In the present work we are particularly interested in the Widom line \cite{XKBetal05,MS10,AKM17} which focuses on thermodynamic properties and represents a conditional boundary between liquid-like and gas-like regions in the supercritical fluid, based on response functions. Thus the Widom line \--- the locus of correlation length maxima emanating from the critical point \cite{XKBetal05}, is treated as the continuation of the coexistence line above the critical point.   
Some thermodynamic response functions, for example, isobaric heat capacity and isothermal compressibility, also exhibit maxima in the supercritical region. In the critical region beyond the critical point the maxima lines of the correlation length and response functions virtually merge into a single line \cite{AKM17} and then diverge from each other as the temperature rise. Thus in the critical region, the Widom line is viewed as the maxima locus of thermodynamic response functions \cite{Proctor20}.

@@

\section{\label{sec:eos}The equation of state: pressure as a function of temperature and chemical potential}

In the present work we take advantage of the results obtained in \cite{KD20,DKRP24arxiv,DKRP24}. In \cite{KD20}, the phase space of collective variables%\footnote{The term "collective variables" is commonly used to refer to a specific category of variables unique to each physical system. In the context of liquid-vapour systems, these collective variables are linked to modes of density deviation from the critical density. This set of collective variables encompasses those which average values are connected to order parameters.Thus, the depiction of the phase transition within the phase space of collective variables appears compelling.} 
is used for calculating the grand partition function of a cell fluid model in the zero-mode approximation and consequently deriving the explicit forms of the equation of state (EoS) both in pressure-temperature-chemical potential terms and pressure-temperature-density terms. The resulting EoSs are applicable in a wide range of temperatures below and above the critical point. In~\cite{DKRP24arxiv,DKRP24}, we used these equations as the basis for the calculation and graphical representation of the thermodynamic response functions (isothermal compressibility, thermal pressure coefficient, thermal expansion) of the cell fluid model with modified Morse potential in the supercritical region.

@@

\section{\label{sec:widom}Crossover line between gas-like and liquid-like structures of the supercritical fluid. The Widom line}

>>>>

\section{Introduction}
A supercritical fluid is a state of matter that occurs when a substance is subjected to temperatures and pressures above its critical point (CP). Below CP the substance exhibits a liquid-gas coexistence. At CP, the distinction between the liquid and gas phases of a substance disappears, and beyond this point, the substance exists in a single continuous supercritical state. Despite the absence of first-order phase transitions above the critical point, fluids exhibit distinct liquid-like and gas-like behavior under supercritical conditions, and display a unique mix of properties. With densities comparable to liquids they possess low viscosity and high diffusivity like gases resulting in high solvent power. Moreover, the supercritical properties are instantly tunable by changing pressure and temperature. This is the reason why supercritical fluids have diverse applications across various industries \cite{KMLetal14}.

Although the traditional liquid-gas phase distinction does not apply in the supercritical region, scientists continue to search for crossover regions or definitive lines that distinguish liquid-like and gas-like behaviors in the phase diagram. Naturally, such boundaries originate from CP and may either vanish away from it or extend infinitely far. Among known approaches to this problem are the Widom line, which represents the locus of correlation length maxima~\cite{FW69}; the Frenkel line~\cite{BGMetal17}, focusing on the dynamics of molecular motion; and the percolation line~\cite{CKS01}, related to spatial structures and marking the threshold where clusters of fluid or density fluctuations form a continuous, system-spanning network.

In the present work, we focus on the Widom line \cite{XKBetal05,MS10,AKM17}, a concept based on thermodynamic response functions that represents a conditional boundary between liquid-like and gas-like regions in supercritical fluids. Thus, the Widom line \--- the locus of correlation length maxima emanating from CP~\cite{XKBetal05} \--- is treated as the continuation of the coexistence line above CP. Moreover, some thermodynamic response functions, such as isobaric heat capacity and isothermal compressibility, also exhibit maxima in the supercritical region. In the critical region beyond the critical point, the maxima lines of the correlation length and these response functions virtually merge into a single line~\cite{AKM17} and then diverge from each other as the temperature increases. Therefore, in the critical region, the Widom line is viewed as the locus of maxima of thermodynamic response functions~\cite{Proctor20}.

@@

\section{\label{sec:eos} The equation of state}

In the present work we take advantage of the results obtained in \cite{KD20,DKRP24arxiv,DKRP24}. In \cite{KD20}, the phase space of collective variables
is used for calculating the grand partition function of a cell fluid model in the zero-mode approximation and consequently deriving the explicit forms of the equation of state (EoS) both in pressure-temperature-chemical potential terms and pressure-temperature-density terms. The resulting EoSs are applicable in a wide range of temperatures below and above the critical point. In~\cite{DKRP24arxiv,DKRP24}, we used these equations as the basis for the calculation and graphical representation of the thermodynamic response functions (isothermal compressibility, thermal pressure coefficient, thermal expansion) of the cell fluid model with modified Morse potential in the supercritical region.

@@

\section{\label{sec:widom}Crossover lines between gas-like and liquid-like behavior of the supercritical fluid.}
